\input{includes/global.tex}
\title{Resume - Boris Kourtoukov}
\date{as of: \today}
\begin{document}
\maketitle

\section{\textcolor{red}{Overview}}

\begin{abstract}
	I focus on learning and experiencing new possibilities in software and hardware. My goals are to remain diverse and join teams that also explore the development of new frontiers in technology. I enjoy crafting unique user experiences, and always iterate on my designs.  My direction is in both academic and product development pursuits, as well as open source hardware and software. \\*[1em]

	I have two years of experience in rapid prototyping of physical computing solutions and five years of working in diverse front end web projects. My front end technologies of choice are SASS and ClojureScript. While physical computing prototypes often start with a version of Arduino that best fits the application. I utilize my experience with a vast array of sensors and various means of building wireless networks in order to create `off the grid' objects. \\*[1em]

\marginnote{
\begin{description}
	\item[\textcolor{gray}{Email}]    \hfill   \\ boriskourt@gmail.com
	\item[\textcolor{gray}{Address}] \hfill   \\ 2-456 Dundas St West Toronto ON
	\item[\textcolor{gray}{Phone}]   \hfill   \\ 1-647-522-2641
\end{description}}
\noindent
\textbf{Front End \& Wearable Technology Developer. }
\begin{description}
	\item[\textcolor{gray}{Portfolio}] \url{http://boris.kourtoukov.com} [Placeholder during revision] 
	\item[\textcolor{gray}{Wearable Technology Projects}] \url{http://boriskourt.com/} 
\end{description}
\end{abstract}



\section{\textcolor{red}{Employment History}}

\subsection{\textcolor{CadetBlue}{\LARGE{Social Body Lab}}} 
\marginnote{\textcolor{gray}{December 2013 ---} \\ \normalsize{Research Assistant \\ Wearables Development}}

Exploring the possibilities in `Prothetic Technologies of Being' as a partnership with Intel Research. The goals of the development project are twofold, create unique wearable experiences and conduct direct user testing in order to asses the quality of those experiences.

\subsection{\textcolor{CadetBlue}{\LARGE{OCADU Continuing Studies}}} 
\marginnote{\textcolor{gray}{April 2014 --- May 2014} \\ \normalsize{Teaching Assistant \\ Physical Computing}}

Provide support to the students with programming and designing wearable devices. Help with the development of soft circuit skills, as well as work with alternative materials. Assist with smooth class operation. 

\subsection{\textcolor{CadetBlue}{\LARGE{CIV-DDD}}} 
\marginnote{\textcolor{gray}{March 2014 ---} \\ \normalsize{Research Assistant \\ Interface Design}}

Analyze and develop possibilities for user interface design in data agnostic sentiment analysis applications. Working on a large scale business to business platform to develop a design language that can persist over multiple product iterations.

\subsection{\textcolor{CadetBlue}{\LARGE{OCADU Fellowship}}} 
\marginnote{\textcolor{gray}{November 2013 ---} \\ \normalsize{Research Fellow \\ Wearables Development}}

Explore wearable interfaces for trans media projects. Focus is on the award winning children's media universe `Time Tremors'. Prototyped devices are intended as open explorations of how wearables can interact with this context.

\subsection{\textcolor{CadetBlue}{\LARGE{WebCanada Inc.}}}
\marginnote{\textcolor{gray}{May 2012 --- September 2013} \\ \normalsize{Front End Devleoper}}

I was one of the main front end developer for WebCanada, my core task was to bridge the gap between the design and development departments and to provide high quality user interface interactions. During my time with WebCanada I have worked largely on high profile hospitality websites for brands like Sheraton, W, Luxury Collection and others. As well as assist with the website production for Concierge Plus, a suite of tools used by Daniels and numerous of other North American property managers. During my stay at WebCanada I had the chance to create a number of interactive displays used in lobbies and at large conferences. 

\subsection{\textcolor{CadetBlue}{\LARGE{StudioFeed}}}
\marginnote{\textcolor{gray}{September 2012 --- December 2012} \\ \normalsize{Co-op \\ Android Developer}}

Work to develop an android based touch interface for a store display based on the Subpac product. Development focused on multi platform web technologies.

\subsection{\textcolor{CadetBlue}{\LARGE{RISE Gaming Inc.}}}
\marginnote{\textcolor{gray}{March 2008 --- June 2011} \\ \normalsize{Product Development }}

I helped manage a game development start up. Helping lead teams of up to forty people.
Worked in a volunteer environment and addressed issues and concerns with the employees in mind. Outlining common goals and constantly working to increase the morale of the team. Lead numerous side projects, ranging from website construction to a physical board game supplement. Produced company websites, and current Epoch Saga game project.


% \subsection{\textcolor{CadetBlue}{\LARGE{Emotional Robots Inc.}}}
% \marginnote{\textcolor{gray}{2009} \\ \normalsize{Web Developer}}

% I have been working on numerous design projects with ERI, ranging from a corporate site to promotional websites for their game titles.

\newpage
\section{\textcolor{red}{Freelance Clients}}

\subsection{\textcolor{CadetBlue}{\LARGE{Situation Lab}}}
\marginnote{\textcolor{gray}{2014} \\ \normalsize{\url{http://situationlab.org/}}}

A project centric website for the Situation Lab, with a focus on a distinct aesthetic and experience.

WordPress CMS. \\*
ClojureScript for interactivity. \\*
Create a simple and intuitive merge between projects and content.\\*

\subsection{\textcolor{CadetBlue}{\LARGE{Fugata Quintet}}}
\marginnote{\textcolor{gray}{2011} \\ \normalsize{\url{http://fugata.co.uk/}}}

A complex website for a British Quintet playing the music of the composer Piazzolla.

WordPress CMS. \\*
Custom SoundCloud integration with WordPress. \\*
Integration with Janrain social login and tracking.\\*
YouTube and Vimeo integration with WordPress, including thumbnail generation and custom video settings.\\*
Fully Responsive Design.

\subsection{\textcolor{CadetBlue}{\LARGE{S2 Games - Tour}}}
\marginnote{\textcolor{gray}{2011}}

Front End Development of an e-sports website for the popular MOBA game Heroes of Newerth.

jQuery development for various dynamic components.\\*
Fully game related theme, integration of art assets into a coherent design and focus on usability without sacrificing the impact of the art assets.

\subsection{\textcolor{CadetBlue}{\LARGE{Chenthooran Nabiarooran}}}
\marginnote{\textcolor{gray}{2011} \\ \normalsize{\url{http://chenthooran.com/}}}

A portfolio website for an illustrator and concept artist.

A unique design intended to showcase digital artwork in an easily visible and interesting manner.
jQuery JavaScript development of custom image displays and galleries. Seamless merge of various content streams in order to create a compelling and easily maintained blog.

\subsection{\textcolor{CadetBlue}{\LARGE{Goldhawk Interactive}}}
\marginnote{\textcolor{gray}{2010}}

Website Design for their Xenonauts game title, intended as a community during their pre-order phase.

Joomla CMS.\\*
Custom Pre-order solution, with user role integration allowing for beta access and other features.\\*
jQuery was used for custom effects that simulated game UI effects.

\newpage
\section{\textcolor{red}{Awards}}
\noindent
2013 --- present 
\subsection{\textcolor{CadetBlue}{\LARGE{Research Fellowship}}}
\marginnote{\normalsize{OCAD University}}
Awarded by OCADU President Sara Diamond to pursue work on a trans media wearable technology project. As well as a personal thesis.

\section{\textcolor{red}{Education}}

\noindent
Fall 2010 --- Spring 2014 \\

\subsection{\textcolor{CadetBlue}{\LARGE{BFA - Digital Futures}}}
\marginnote{\normalsize{OCAD University}}

Toronto, ON \\*

Part of the first wave of this major program at OCAD. Given the great opportunity to interact with the program on a different level, connect with instructors and shape the future curriculum.
Work focused on Data Visualization, Physical Computing, the Wearables as well as Human Factors and Inclusive Design.

\end{document}